Appendix

### 2020-03-16 manuscript/appendix.Rmd
cleanup

```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watersehd clay content and lake TN concentration. Vertical dashed line shows transition between a positive and a negative correlation (r) between the two variables. Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3}
# Why was the clay coefficient negative in the TN model?
# re_brms <- readRDS("data/mcmc/re_brms.rds")
# re_brms[[8]]$formula
dt       <- # readRDS("data/dt.rds") %>%
  readRDS("../data/dt_scaled.rds") %>%
  dplyr::select(clay_pct, hu12_ppt_mean, hu12_baseflow_mean, 
                buffer_cultivated_crops, iwsla_ratio, soil_org_carbon,
                wetlands,
                maxdepth, ag, tn, lagoslakeid)

>>>>

```{r clay-nonlinear, fig.cap = "Scatterplot showing the non-linear relationship between watershed clay content and lake TN concentration. Vertical dashed line shows transition between a positive and a negative correlation (r) between the two variables. Solid red line shows the fit of a generalized additive model from the mgcv R package.", warning=FALSE, echo = FALSE, eval=TRUE, fig.height=3, fig.width=3.3, message=FALSE}
library(magrittr)
# Why was the clay coefficient negative in the TN model?
# re_brms <- readRDS("data/mcmc/re_brms.rds")
# re_brms[[8]]$formula
dt       <- # readRDS("data/dt.rds") %>%
  readRDS("../data/dt_scaled.rds") %>%
  dplyr::select(clay_pct, hu12_ppt_mean, hu12_baseflow_mean, 
                buffer_cultivated_crops, iwsla_ratio, soil_org_carbon,
                wetlands,
                maxdepth, ag, tn, lagoslakeid)
